\clearpage
% Inserisce la voce di questo capitolo nell'indice
\addcontentsline{toc}{chapter}{Bibliografia}
\begin{thebibliography}{9}
\bibitem{OSSINI}
	M. Zec, M. Mikuc.
	\emph{Operating System Support for Integrated Network Emulation in IMUNES}, to appear in Proceedings of the 1st Workshop on Operating System and Architectural Support for the on demand IT InfraStructure / ASPLOS-XI, Boston, October 2004.

\bibitem{MVNL08}
	Jean-Vincent Loddo, Luca Saiu.
	\emph{Marionnet: A Virtual Network Laboratory and Simulation Tool}, SimulationWorks, Marseille (France), 2008

\bibitem{QUATC05}
	Fabrice Bellard.
	\emph{QEMU, a Fast and Portable Dynamic Translator}, 2005 USENIX Annual Technical Conference.

\bibitem{VNUMLT}
	\emph{VNUML Tutorial}, www.dit.upm.es/vnumlwiki/index.php/Tutorial.

\bibitem{VNUMLGUI}
	\emph{VNUMLGUI}, pagesperso.erasme.org/michel/vnumlgui.

\bibitem{NETKIT}
	\emph{Netkit}, www.netkit.org.

\bibitem{IRPI07}
	Massimo Rimondini.
	\emph{Interdomain Routing Policies in the Internet: Inference and Analysis}, A thesis presented by Massimo Rimondini in partial fulfillment of the requirements for the degree of Doctor of Philosophy in Computer Science and Engineering, Roma Tre University, Dept. of Informatics and Automation, March 2007.

\bibitem{ECNN07}
	Massimo Rimondini.
	\emph{Emulation of Computer Networks with Netkit}, Tutorial held during the 4th International Workshop on Internet Performance, Simulation, Monitoring and Measurement (IPS MoMe 2006) in Salzburg, February 2006.

\bibitem{AUPL04}
	Craig Larman.
	\emph{Applying UML and Patterns: An Introduction to Object-Oriented Analysis and Design and Iterative Development (3rd Edition)}, Prentice Hall PTR, October 2004.

\bibitem{SSA06}
	Nick Rozanski, Eoin Woods
	\emph{Software System Architecture: Working With Stakeholders Using Viewpoints and Prespectives}, Addison Wesley

\end{thebibliography}
